---
title: 'Comps: Econ Anxiety & Authoritarianism'
subtitle: "The Effect of Economic Anxiety on Support for Authoritarianism"
author: "Shane Zerr"
date: "May 1st, 2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

#R Prep
##Settings
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Packages
```{r, error=FALSE, message=FALSE}
library(tidyverse)
library(car)
library(stats)
library(DescTools)
library(ggplot2)
library(foreign)
library(arm)
library(stargazer)
library(lm.beta)
library(lmtest)
library(sandwich)
library(mosaic)
library(weights)
library(pewmethods)
library(anesrake)
```

##Import Data
```{r, error=FALSE, message=FALSE}
#This is the Trump-era, pre-covid data.
orig.anes <- read_csv("~/Documents/R Studio/COMPS/Data/anes_pilot_2018.csv")

#This is my Biden-era, covid data.
orig.qualtrics <- read_csv("~/Documents/R Studio/COMPS/Data/Qualtrics_Data.csv")

#Demographic crosstabs for reweighing the qualtrics data.
data("acs_2017_excerpt")
```

##Recode
```{r, error=FALSE, message=FALSE}
##Note: dplyr clashes with MASS, so I have to use dplyr::select
anes <- dplyr::select(orig.anes, finworry, strlead, strpres, econ12mo, finpar1, finpar2, improve1, improve2, educ, gender, birthyr, whiteid, rr1, weight, pid7x)

qualtrics <- dplyr::select(orig.qualtrics, ResponseId, covid_anxiety, strlead, strpres, finworry, econ12mo, finpar1, finpar2, improve, educ, gender, birthyr, white, whiteid, rr1)
```

###Recode for Descriptive Stats
```{r}
#New variable Strong Leader
anes.stat <- anes
anes.stat$strlead <- anes$strlead
#Re-label responses according to codebook
anes.stat$strlead[anes.stat$strlead==-1] <- NA

#New variable Strong President
anes.stat$strpres <- anes$strpres
#Re-label responses according to codebook
anes.stat$strpres[anes.stat$strpres==-1] <- NA
anes.stat$strpres[anes.stat$strpres==-7] <- NA

#New variable Financial Improvement
anes.stat$improve1 <- anes$improve1
#Re-label responses according to codebook
anes.stat$improve1[anes.stat$improve1==-1] <- NA

#New variable Financial Improvement
anes.stat$improve2 <- anes$improve2
#Re-label responses according to codebook
anes.stat$improve2[anes.stat$improve2==-1] <- NA

#New variable combined improve
anes.stat$improve <- NA
anes.stat$improve <- ifelse(is.na(anes.stat$improve1) == TRUE, 
                            anes.stat$improve2, anes.stat$improve1)

#New variable Economy 12 Months
anes.stat$econ12mo <- anes$econ12mo
#Re-label responses according to codebook
anes.stat$econ12mo[anes.stat$econ12mo==-1] <- NA
anes.stat$econ12mo[anes.stat$econ12mo==-7] <- NA

#New variable Finance Parents 1
anes.stat$finpar1 <- anes$finpar1
#Re-label responses according to codebook
anes.stat$finpar1[anes.stat$finpar1==-1] <- NA

#New variable Finance Parents 1
anes.stat$finpar2 <- anes$finpar2
#Re-label responses according to codebook
anes.stat$finpar2[anes.stat$finpar2==-1] <- NA

#New variable Economy 12 Months
anes.stat$finworry <- anes$finworry

#New variable Economy 12 Months
anes.stat$educ <- anes$educ

#New variable Economy 12 Months
anes.stat$birthyr <- anes$birthyr

#New variable Economy 12 Months
anes.stat$gender <- anes$gender

#New variable White Identity
anes.stat$whiteid <- anes$whiteid
anes.stat$whiteid[anes.stat$whiteid==-1] <- NA
anes.stat$whiteid[anes.stat$whiteid==-7] <- NA

#New variable Racial Resentment 1
anes.stat$rr1 <- anes$rr1
anes.stat$rr1[anes.stat$rr1==-1] <- NA

#New variable ~Rural
anes.stat$pid7x <- anes$pid7x
anes.stat$pid7x[anes.stat$pid7x==-7] <- NA

#New variable Statistical Weight
anes.stat$weight <- anes$weight

#Re-label responses according to codebook
qualtrics$gender[qualtrics$gender==3] <- NA
qualtrics$gender[qualtrics$gender==4] <- NA

#Re-label responses according to codebook
qualtrics$white[qualtrics$white==4] <- NA
```

###Recode ACS Crosstabs & Qualtrics prep.
```{r, echo=FALSE}
#Rename ACS tibble vectors to match my data sets
acs_2017_excerpt <- rename(acs_2017_excerpt, gender = sex)
acs_2017_excerpt <- rename(acs_2017_excerpt, educ = receduc)
acs_2017_excerpt <- rename(acs_2017_excerpt, birthyr = recage)

#Recoding Qualtrics to match my dummy variables
qualtrics.weight <- qualtrics
qualtrics.weight$gender[qualtrics.weight$gender=="1"] <- "Male"
qualtrics.weight$gender[qualtrics.weight$gender=="2"] <- "Female"

qualtrics.weight$educ[qualtrics.weight$educ=="1"] <- "HS grad or less"
qualtrics.weight$educ[qualtrics.weight$educ=="2"] <- "HS grad or less"
qualtrics.weight$educ[qualtrics.weight$educ=="3"] <- "Some coll/Assoc degree"
qualtrics.weight$educ[qualtrics.weight$educ=="4"] <- "Some coll/Assoc degree"
qualtrics.weight$educ[qualtrics.weight$educ=="5"] <- "Coll+"
qualtrics.weight$educ[qualtrics.weight$educ=="6"] <- "Coll+"

qualtrics.weight$birthyr[qualtrics.weight$birthyr <= 1956] <- "65+"
qualtrics.weight$birthyr[qualtrics.weight$birthyr > 1956 & qualtrics.weight$birthyr <= 1966] <- "55-64"
qualtrics.weight$birthyr[qualtrics.weight$birthyr > 1966 & qualtrics.weight$birthyr <= 1976] <- "45-54"
qualtrics.weight$birthyr[qualtrics.weight$birthyr > 1976 & qualtrics.weight$birthyr <= 1986] <- "35-44"
qualtrics.weight$birthyr[qualtrics.weight$birthyr > 1986 & qualtrics.weight$birthyr <= 1996] <- "25-34"
qualtrics.weight$birthyr[qualtrics.weight$birthyr > 1976 & qualtrics.weight$birthyr <= 2003] <- "18-24"

#Check qualtrics.weight df type
class(qualtrics.weight)

#If tbl, run below code to coerce to data.frame
qualtrics.weight <- as.data.frame(qualtrics.weight)
class(qualtrics.weight)  #If this works as intended, it should print: [1] "data.frame"
                         #anesweight cannot compute weights if the survey data set is a tbl.  

#Transform data from charachter to factor. Boy is anesweight picky.  
qualtrics.weight$gender <- as.factor(qualtrics.weight$gender) 
qualtrics.weight$educ <- as.factor(qualtrics.weight$educ) 
qualtrics.weight$birthyr <- as.factor(qualtrics.weight$birthyr) 


```

###Creating Weights with ANES Rake
```{r}
#Create Target Weighting List
target <- with(acs_2017_excerpt, list(
  educ = wpct(educ, weight),
  gender  = wpct(gender, weight),
  birthyr  = wpct(birthyr, weight)
))

#Check List
str(target)

#Compare to Qualtrics data, if you want.  Qualtrics skews both male and educated, for example
wpct(qualtrics.weight$educ)
wpct(qualtrics.weight$gender)
wpct(qualtrics.weight$birthyr)

#Iteratively rake until convergence. 
raking <- anesrake(target,
                    qualtrics.weight,
                    qualtrics.weight$ResponseId,
                    cap=10,                      # Maximum allowed weight per iteration
                    choosemethod = "total",       # How are parameters compared for selection?
                    type = "pctlim",              # What selection criterion is used?
                    pctlim = 0.05                 # Threshold for selection
                     )

#Raking summary
raking_summary <- summary(raking)

#What variables were used for raking?
raking_summary$raking.variables

#Apply weights into qualtrics data.  
qualtrics$weight <- raking$weightvec
```

###Recode for WhiteID
```{r}
#Create new data frame to recode people who are not white as having no white identity..
qualtrics.whiteid <- qualtrics

#Create new temp column with value <
qualtrics.whiteid$temp <- 5
qualtrics.whiteid$whiteid <- ifelse(is.na(qualtrics.whiteid$whiteid) == TRUE, 
                                    qualtrics.whiteid$temp, qualtrics.whiteid$whiteid)
```

#Model
##ANES Model with Prejudice & Weight
###Strpres w/ Prejudice & Weight
```{r}
strpres.anes <- lm(strpres ~ econ12mo + finworry + improve + finpar2 +  whiteid + rr1 + educ + gender + birthyr, data=anes.stat, weights=weight)

stargazer(strpres.anes, title="Effect of Financial Anxiety on Support for Unchecked President", 
          align=TRUE, dep.var.labels=c("Support for Unchecked President"), 
          covariate.labels=c("Short-term Systemic", 
                             "Short-term Personal", 
                             "Long-term Systemic", 
                             "Long-term Personal", 
                             "White Identiy", 
                             "Racial Resentment", 
                             "Education Level", 
                             "Gender", 
                             "Age", 
                             "Demographic Re-weighting"),
                    omit.stat = c("ser", "f"), type= "text")
```

Strlead lmbeta
```{r}
lm.beta(strpres.anes)
```


###Strlead w/ Prejudice & Weight
```{r}
strlead.anes <- lm(strlead ~ econ12mo + finworry + improve + finpar1 +  whiteid + rr1 + educ + gender + birthyr, data=anes.stat, weights=weight)

stargazer(strlead.anes, title="Effect of Financial Anxiety on Support for Authoritarian Tendencies", 
          align=TRUE, dep.var.labels=c("Support for Strong Leader who Bends Rules"), 
          covariate.labels=c("Short-term Systemic", 
                             "Short-term Personal", 
                             "Long-term Systemic", 
                             "Long-term Personal", 
                             "White Identiy", 
                             "Racial Resentment", 
                             "Education Level", 
                             "Gender", 
                             "Age"),
                    omit.stat = c("ser", "f"), type= "text")
```

Strlead lmbeta
```{r}
lm.beta(strlead.anes)
```

##Qualtrics Model with Prejudice & Weight
###Strpres w/ Prejudice & Weight
```{r}

#                         !!!!!Note to Shane!!!!
  #Make sure to choose finpar1 or finpar2 or just combine them into an aggregate finpar measure.  
    #I just included both slightly different wordings in the qualtrics to be able to direcly compare with ANES results in 1:1. 

strpres.qualtrics <- lm(strpres ~ econ12mo + finworry + improve + finpar2 +  whiteid + rr1 + educ + gender + birthyr, data=qualtrics.whiteid, weights=weight)


stargazer(strpres.qualtrics, title="Effect of Financial Anxiety on Support for Unchecked President", 
          align=TRUE, dep.var.labels=c("Support for Unchecked President"), 
          covariate.labels=c("Short-term Systemic", 
                             "Short-term Personal", 
                             "Long-term Systemic", 
                             "Long-term Personal", 
                             "White Identiy", 
                             "Racial Resentment", 
                             "Education Level", 
                             "Gender", 
                             "Age"),
                    omit.stat = c("ser", "f"), type= "text")
```

Strlead lmbeta
```{r}
lm.beta(strpres.qualtrics)
```


###Strlead w/ Prejudice & Weight
```{r}
strlead.qualtrics <- lm(strlead ~ finworry + econ12mo + improve + finpar1 +  whiteid + rr1 + educ + gender + birthyr, data=qualtrics.whiteid, weights=weight)

stargazer(strlead.qualtrics, title="Effect of Financial Anxiety on Support for Authoritarian Tendencies", 
          align=TRUE, dep.var.labels=c("Support for Strong Leader who Bends Rules"), 
          covariate.labels=c("Short-term Systemic", 
                             "Short-term Personal", 
                             "Long-term Systemic", 
                             "Long-term Personal", 
                             "White Identiy", 
                             "Racial Resentment", 
                             "Education Level", 
                             "Gender", 
                             "Age", 
                             "Demographic Re-weighting"),
                    omit.stat = c("ser", "f"), type= "text")
```

Strlead lmbeta
```{r}
lm.beta(strlead.qualtrics)
```

#Statistics Tests
##Strpres.anes
Coefficient Plot
```{r, fig.show='show'}
arm::coefplot(strpres.anes, 
              xlab = "OLS Multivar Regression Model: Strpres & ANES" , mar = c(4, 4, 5, 6), xlim = c(-1, 1))
```

Multicollinearity & VIF
```{r}
# 2. Calculate the VIF for model: VIF = 1 (Not correlated); 1 < VIF < 5 (Moderately correlated); VIF >=5 (Highly correlated)
vif(strpres.anes)
# Take the square root of the VIF to standardize it in terms of standard errors
# Shows the impact of multicollinearity on hypothesis testing inferences
sqrt(vif(strpres.anes))
# Compare the standardized VIF to the threshold of 2.5 
sqrt(vif(strpres.anes)) > 2.5 
# If true, then this indicates that the standard errors are inflated by at least double due to the presence of multicollinearity. If false, then this indicates that the errors are inflated by less than 2.5x. Thus avoiding even a conservative threshold for problematic multicolinearity.
```
Thus, the StrLead Model passes VIF requirements.

##Strlead.anes
Coefficient Plot
```{r, fig.show='show'}
arm::coefplot(strlead.anes, 
              xlab = "OLS Multivar Regression Model: Strlead & ANES" , mar = c(4, 4, 5, 6), xlim = c(-1, 1))
```

Multicollinearity & VIF
```{r}
# 2. Calculate the VIF for model: VIF = 1 (Not correlated); 1 < VIF < 5 (Moderately correlated); VIF >=5 (Highly correlated)
vif(strlead.anes)
# Take the square root of the VIF to standardize it in terms of standard errors
# Shows the impact of multicollinearity on hypothesis testing inferences
sqrt(vif(strlead.anes))
# Compare the standardized VIF to the threshold of 2.5 
sqrt(vif(strlead.anes)) > 2.5 
# If true, then this indicates that the standard errors are inflated by at least double due to the presence of multicollinearity. If false, then this indicates that the errors are inflated by less than 2.5x. 
```


##Strpres.qualtrics
Coefficient Plot
```{r, fig.show='show'}
arm::coefplot(strpres.qualtrics, 
              xlab = "OLS Multivar Regression Model: Strpres & ANES" , mar = c(4, 4, 5, 6), xlim = c(-1, 1))
```

Multicollinearity & VIF
```{r}
# 2. Calculate the VIF for model: VIF = 1 (Not correlated); 1 < VIF < 5 (Moderately correlated); VIF >=5 (Highly correlated)
vif(strpres.qualtrics)
# Take the square root of the VIF to standardize it in terms of standard errors
# Shows the impact of multicollinearity on hypothesis testing inferences
sqrt(vif(strpres.qualtrics))
# Compare the standardized VIF to the threshold of 2.5 
sqrt(vif(strpres.qualtrics)) > 2.5 
# If true, then this indicates that the standard errors are inflated by at least double due to the presence of multicollinearity. If false, then this indicates that the errors are inflated by less than 2.5x.
```

##Strlead.qualtrics
Coefficient Plot
```{r, fig.show='show'}
arm::coefplot(strlead.qualtrics, 
              xlab = "OLS Multivar Regression Model: STRPRES & ANES" , mar = c(4, 4, 5, 6), xlim = c(-1, 1))
```

Multicollinearity & VIF for 
```{r}
# 2. Calculate the VIF for model: VIF = 1 (Not correlated); 1 < VIF < 5 (Moderately correlated); VIF >=5 (Highly correlated)
vif(strlead.qualtrics)
# Take the square root of the VIF to standardize it in terms of standard errors
# Shows the impact of multicollinearity on hypothesis testing inferences
sqrt(vif(strlead.qualtrics))
# Compare the standardized VIF to the threshold of 2.5 
sqrt(vif(strlead.qualtrics)) > 2.5 
# If true, then this indicates that the standard errors are inflated by at least double due to the presence of multicollinearity. If false, then this indicates that the errors are inflated by less than 2.5x.
```
